### 2022-10-09 README.Rmd
reliability!

<!-- - Write vignettes for tests of the app -->
<!-- - Write vignette for medication data -->
<!-- - Replication with AB's group -->
<!-- - Incorporate suppression of unreliable estimates -->
<!-- - Documentation/demos for R functions used in the app -->
<!-- - Definitions/notes for all BP variables (table S1 in manuscript) -->
<!-- - Tutorial videos -->
<!-- - Do we need to use AF weights? -->

>>>>

<!-- - Write vignettes for tests of the app -->
<!-- - Write vignette for medication data -->
<!-- - Replication with AB's group -->
<!-- - Incorporate suppression of unreliable estimates -->
<!-- - Documentation/demos for R functions used in the app -->
<!-- - Tutorial videos -->
<!-- - Do we need to use AF weights? -->
